Covariate analysis of MAYO reprocessed transcripts (with TMM normalisation and covariates adjusted)

### 2017-09-08 code/Rmd/MAYO_REPROCESSED_ISOFORM.Rmd
Modified markdown to process MAYO isoform

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=10, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>%
                   dplyr::filter(Comparison == 'Control-AD'), 
                 aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(BrainRegion.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')

pl[[2]] = ggplot(DE %>%
                   dplyr::filter(Comparison == 'Control-AD'), 
                 aes(x = percentage_gc_content, y = logFC, color = Direction)) + geom_point()
pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gc_content, y = logFC))
pl[[2]] = pl[[2]] + facet_grid(BrainRegion.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[2]] = pl[[2]] + theme(legend.position = 'top')

pl[[3]] = ggplot(DE %>%
                   dplyr::filter(Comparison == 'Control-AD'), 
                 aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
pl[[3]] = pl[[3]] + facet_grid(BrainRegion.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[3]] = pl[[3]] + theme(legend.position = 'top')

multiplot(plotlist = pl, cols = 3)
```

@@

# Store logCPM
VOOM.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Tx.ID') %>%
  write.table(file = 'MAYO_CBE_TCX_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('MAYO_CBE_TCX_logCPM.tsv', name = 'TPM (filtered)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store all model fits
save(list = 'all.fit', file = 'MAYO_CBE_TCX_allfits.RData')
AFIT_OBJ = File('MAYO_CBE_TCX_allfits.RData', 
                name = 'All model fits (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(AFIT_OBJ) = annotations(CODE)
annotations(AFIT_OBJ)$dataSubType = 'modelFits'
AFIT_OBJ = synStore(AFIT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (estimated)                         |  `r ECOUNT_OBJ$properties$id`    |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

>>>>

@@

# Store logCPM
VOOM.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Tx.ID') %>%
  write.table(file = 'MAYO_CBE_TCX_tpm.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('MAYO_CBE_TCX_TPM.tsv', name = 'TPM (filtered)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store all model fits
save(list = 'all.fit', file = 'MAYO_CBE_TCX_allfits.RData')
AFIT_OBJ = File('MAYO_CBE_TCX_allfits.RData', 
                name = 'All model fits (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(AFIT_OBJ) = annotations(CODE)
annotations(AFIT_OBJ)$dataSubType = 'modelFits'
AFIT_OBJ = synStore(AFIT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (estimated)                         |  `r ECOUNT_OBJ$properties$id`    |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
